Red bus, blue bus; and the choice between Florida, California, and Florida plus a nickel

### 2022-07-07 inst/red_bus_blue_bus.Rmd
red bus blue bus references
more work on red bus/blue bus

---
title: "Red bus, blue bus"
output: pdf_document
bibliography: chess.bib
---

@@

The red bus-blue bus problem was originally stated by
@davidson1970.  The other one was the holiday problem.

@@

THERE IS ALSO THE THING WITH THE HOLIDAY IN CALIFORNIA AND THE HOLIDAY
IN FLORIDA AND THE HOLIDAY IN FLORIDA PLUS TEN BUCKS

@@

{F,FN,C,CN} :  (F,F+N,C,C+N)/(2F+2C+2N)  ??????????????

@@

{F,FN,FC,CN}  :  p(F)  = F/(F+C) * F/(F+N)
              :  p(FN) = F/(F+C) * N/(F+N) 
              :  p(C)  = C/(F+C) * C/(C+N) 
              :  p(CN) = C/(F+C) * N/(C+N)

@@

{F,C,CN}    :  p(F)  = F/(F+C)
            :  p(C)  = C/(F+C) * C/(C+N)
            :  p(CN) = C/(F+C) * N/(C+N)

@@

L = L(C,B,red,blue)

>>>>

---
title: "Red bus, blue bus; and the choice between Florida, California, and Florida plus a nickel"
output: pdf_document
bibliography: chess.bib
---

@@

In this short discussion document I discuss three related problems:

* The red bus-blue bus problem
* Debussy-Beethoven problem
* Holiday problem

The red bus-blue bus problem was originally stated by @chipman1960 and
discussed by @davidson1970 and @alvo2010 (page 153).
Debussy-Beethoven was @debreu1960.  I have lost the original reference
to the Holiday problem.

@@

@@

{F,FN,C,CN} :  (F,F+N,C,C+N)/(2F+2C+2N)  ??????????????
```

@@

```
{F,FN,FC,CN}  :  p(F)  = F/(F+C) * F/(F+N)
              :  p(FN) = F/(F+C) * N/(F+N) 
              :  p(C)  = C/(F+C) * C/(C+N) 
              :  p(CN) = C/(F+C) * N/(C+N)
```

@@

```
{F,C,CN}    :  p(F)  = F/(F+C)
            :  p(C)  = C/(F+C) * C/(C+N)
            :  p(CN) = C/(F+C) * N/(C+N)
```

@@

```
L = L(C,B,red,blue)
